On the relation of the entanglement spectrum to the Zak-phase

### 2020-08-31 version2/draft.tex
Add files via upload

Note also that we are computing the Chern number in the torus defined by $(\Phi,k_y)$. It seems a bit weird to mix both flux and momentum but it works in the end. If we were to introduce another flux in the other direction the system would no longer be effectively 1D so I don't know if everything we do would still apply in the same way or if it would provide any advantage.´ }

>>>>

Note also that we are computing the Chern number in the torus defined by $(\Phi,k_y)$. It seems a bit weird to mix both flux and momentum but it works in the end. If we were to introduce another flux in the other direction the system would no longer be effectively 1D so I don't know if everything we do would still apply in the same way or if it would provide any advantage. }
